%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
{Wayfair} % Organization 
{iOS Core Developer - Summer Internship} % Job title
{Boston, MA} % Location
{Summer Internship 2018} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Led a team in the development of an iMessage extension to enable native sharing of saved 3D "View In Room" configurations.}
		\item {Designed a smooth, intuitive user experience for product selection and sharing for both iPhone and iPad.}
	\end{cvitems}
}

  \cventry
{Personal Software Development Project} % Organization 
{Stronghold - macOS Security Configuration Tool} % Job title
{Champaign, IL} % Location
{March 2018} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Developed and open-sourced a command line tool that walked a user through securely configuring macOS.}
		\item{Gained some depth of knowledge into macOS security architecture.} 
		\item {Helped secure over 4000 macs.}
	\end{cvitems}
}
%---------------------------------------------------------
  \cventry
    {University of Illinois - College of Engineering} % Organization 
    {Course Infrastructure Developer - Plagiarism Detection Software} % Job title
    {Champaign, IL} % Location
    {Jan. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing plagiarism detection software that relies on behavioral indicators, code style metrics, and code structure metrics.}
        \item {Became proficient with the ANTLR and NLTK libraries. Used them effectively for AST parsing and lexical analysis.}
      \end{cvitems}
    }

%---------------------------------------------------------
%---------------------------------------------------------
  \cventry
{University of Illinois - College of Engineering} % Organization 
{Lab Instructor for Intro to Computer Science} % Job title
{Champaign, IL} % Location
{Aug. 2017 - Dec. 2017} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Taught fundamentals of Java programming and algorithm analysis in weekly two-hour lab sections.}
		\item {Worked one-on-one with students during office hours; moderated course forum.}
	\end{cvitems}
}
%---------------------------------------------------------
\end{cventries}
