%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Open Source Software}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{Developer-friendly macOS security configuration tool} % Organization 
{Stronghold} % Job title
{Champaign, IL} % Location
{2018} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Developed a command line interface that guides users through step-by-step secure configuration for macOS.}
		\item {Secured the workstations of more than 7500 mac users, and earned over 250 stars on GitHub.}
		\item{Gained familiarity with macOS security architecture.} 
	\end{cvitems}
}
\cventry
{Bitcoin trading and charting software that uses ML to forecast price movements} % Organization 
{Bitvision} % Job title
{Champaign, IL} % Location
{2018} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Implemented a text analysis pipeline to analyze the sentiment of Bitcoin-related headlines for an automated trading algorithm.}
		\item {Designed and built a command line user interface using Blessed.js.}
		\item {Worked with another developer to integrate the Python backend with the Javascript frontend.}
	\end{cvitems}
}

\cventry
{Chrome extension to measure trends in sentiment of Messenger conversations} % Organization 
{Typesense} % Job title
{Champaign, IL} % Location
{2018} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Worked with a team to build the first prototype which won "Best Healthcare-related Hack" at HackIllinois 2018.}
		\item {Wrote a rolling window algorithm that analyzes change in sentiment over a set of messages using the VADER library.}
	\end{cvitems}
}
%\cventry
%{Open Source Software} % Organization 
%{Shallow-Backup} % Job title
%{Champaign, IL} % Location
%{2018} % Date(s)
%{
%	\begin{cvitems} % Description(s) of experience/contributions/knowledge
%		\item {Developed a utility to compress package manager libraries to simple text files and recreate the environment from those text files.}
%		\item {Used by over 1000 developers to minimize system backup size.}
%	\end{cvitems}
%} 


%---------------------------------------------------------
%---------------------------------------------------------
\end{cventries}
