%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{ProdSec Native Assurance — Facebook} % Organization
{Security Engineer} % Job title
{Seattle, WA} % Location
{June 2022 - Present} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Built continuous integration testing systems to detect security vulnerabilities and prevent security regressions in PortalOS.}
		\item {Created threat models and documented attack surfaces in order to effectively prioritize security review efforts.}
		\item {Conducted security reviews of high-risk surfaces. Created  mitigations that eliminated vuln classes.}
		\item {Triaged whitehat reports,  awarded bug bounty payouts, and created proof of concept exploits.}
		%  \item {Worked on a team to create proof of concept Stella exploitation exercise}
	\end{cvitems}
}
%---------------------------------------------------------
\cventry
{Red Team X, Incident Detection and Response (IDR), ProdSec — Facebook} % Organization
{Rotational Security Engineer} % Job title
{Remote} % Location
{Dec 2021 - June 2022} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Expanded EDR capabilities, improved case investigation tooling, and triaged the IDR incident queue.}
		\item {Analyzed Unity engine to create signatures that could be used to hunt for and identify malware in 3P Oculus apps.}
		\item {Expanded coverage of automated vuln detection tools, resulting in vulns being detected and remediated before being deployed.}
		\item {Coordinated incident response at company-wide scale. Led day 0 log4j response -- patched critical services, including Messenger.}
	\end{cvitems}
}
%---------------------------------------------------------
\cventry
{Portal Kernel Security — Facebook} % Organization
{Software Engineer} % Job title
{Remote} % Location
{Sept 2020 - Dec 2021} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Led hardening efforts for PortalOS by using sanitizers, fuzzers, and modern security mitigations.} 
		\item {Built the first PoC fuzzing harnesses for Portal using AFL. Used UBSAN / ASAN / MSAN / TSAN to find hundreds of bugs, including a set of memory corruption vulnerabilities in PJSIP: \textit{CVE-2022-39244 (9.8 CVSS)}.}
		\item {Added Portal support to manufacturing platform. Built HSM integration, logging for security auditing, auto-escalation policies.}
		\item {Created factory resource monitoring pipelines to eliminate entire classes of manufacturing issues, saving millions of dollars.}
		%\item {Implemented factory monitoring and auto-triage systems that eliminated entire classes of manufacturing SEVs.}
		%\item {Docker-based local replication of our manufacturing environment, so we can test our manufacturing lines in house before sending them to the factory.}
	\end{cvitems}
}
%---------------------------------------------------------
\cventry
{Authentication e2e Team — Facebook} % Organization
{Software Engineering Intern} % Job title
{Menlo Park, CA} % Location
{Summer 2019} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Worked on a team securing authentication across the entire Facebook universe of apps, including Whatsapp and Instagram.}
		\item {Designed, implemented and deployed a solution to prevent internal attackers from obtaining access to user accounts and data.}
		\item {Improved monitoring and auditing capabilities in C++ for more than 1 billion daily authentication attempts.}
	\end{cvitems}
}
%---------------------------------------------------------
%\cventry
%{\textnormal{i}OS Core Team — Wayfair} % Organization
%{iOS Software Engineering Intern} % Job title
%{Boston, MA} % Location
%{Summer 2018} % Date(s)
%{
%	\begin{cvitems} % Description(s) of tasks/responsibilities
%		\item {Developed a furniture sharing iMessage extension in Swift for the Wayfair iOS app, which is used by 200k daily users.}
%		%\item {Built an interface for over 200,000 daily Wayfair customers to share furniture recommendations over iMessage.}
%		%\item {Addressed challenging iOS security issues, balancing customer experience and data security.}
%		\item {Led the Community Coding Day event and made a curriculum to teach 200+ middle schoolers basic CS concepts.}
%	\end{cvitems}
%}
%---------------------------------------------------------
%\cventry
%{Course Infrastructure Team — University of Illinois — CS Department} % Organization
%{Developer — Plagiarism Detection Software} % Job title
%{Champaign, IL} % Location
%{Jan. 2018 - May 2019} % Date(s)
%{
%	\begin{cvitems} % Description(s) of tasks/responsibilities
%		\item {Developed plagiarism detection software that applies machine learning to code metrics and behavioral indicators.}
%		\item {Analyzed natural language and performed static analysis using the NLTK and ANTLR libraries.}
%		% \item {Researched transferability of key lessons to problems of intrusion and malware detection.}
%	\end{cvitems}
%}
%---------------------------------------------------------
%\cventry
%{University of Illinois — CS Department} % Organization
%{Lab Instructor — Java Programming Fundamentals} % Job title
%{Champaign, IL} % Location
%{Aug. 2017 - Dec. 2017} % Date(s)
%{
%	\begin{cvitems} % Description(s) of tasks/responsibilities
%		\item {Taught fundamentals of Java programming, algorithm design, and data structures in weekly two-hour lab sections.}
%		\item {Worked one-on-one with students in office hours to help them develop a deeper understanding of computer science.}
%	\end{cvitems}
%}
%---------------------------------------------------------
\end{cventries}
