%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Open Source Software}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{A collection of techniques used in Linux and macOS malware} % Organization
{Malware Techniques} % Job title
{Champaign, IL} % Location
{2019} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Researched Linux and macOS malware, and implemented anti-VM, anti-debugging and anti-analysis measures.}
		\item {Implemented a Linux kernel-level rootkit that was undetected by standard rootkit checkers.}
	\end{cvitems}
}

\cventry
{Developer-friendly command line utility} % Organization
{Stronghold — macOS Security Configuration Tool} % Job title
{Champaign, IL} % Location
{2018} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Developed a command line interface that guides users through step-by-step secure configuration for macOS.}
		\item {Secured the workstations of more than 20,000 macOS users and earned over 500 stars on GitHub.}
		\item {Gained familiarity with macOS security architecture.}
	\end{cvitems}
}

\cventry
{Linguistic analysis and machine learning applied to Bitcoin price forecasting} % Organization
{Bitvision — Machine Learning-based Trading Platform} % Job title
{Champaign, IL} % Location
{2018} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Implemented a text analysis pipeline to analyze news headline sentiment for an automated trading algorithm.}
		\item {Designed and built a command line user interface using Blessed.js.}
		\item {Worked with a development partner to integrate the Python backend with the Javascript frontend.}
	\end{cvitems}
}

% \cventry
% {Chrome extension to measure trends in sentiment of Messenger conversations} % Organization
% {Typesense — Linguistic Analysis Tool} % Job title
% {Champaign, IL} % Location
% {2018} % Date(s)
% {
% 	\begin{cvitems} % Description(s) of tasks/responsibilities
% 		\item {Designed a system to help patients with autism understand the emotions of others when talking online.}
% 		\item {Worked with a team to build a prototype that won "Best Healthcare-related Hack" at HackIllinois 2018.}
% 		\item {Wrote a rolling window algorithm that analyzes change in sentiment over a set of messages using the VADER library.}
% 	\end{cvitems}
% }

%\cventry
%{Open Source Software} % Organization
%{Shallow-Backup} % Job title
%{Champaign, IL} % Location
%{2018} % Date(s)
%{
%	\begin{cvitems} % Description(s) of experience/contributions/knowledge
%		\item {Developed a utility to compress package manager libraries to simple text files and recreate the environment from those text files.}
%		\item {Used by over 1000 developers to minimize system backup size.}
%	\end{cvitems}
%}

\end{cventries}
